\chapter*{List of Abbreviations}
\addcontentsline{toc}{chapter}{List of Abbreviations}

\begin{leftitemize}
    \item[UKH]  University of Kurdistan Hewlêr.
    \item[STDC] Student Talent Development Center.
    \item[PAL]  Peer Assisted Learning.
    \item[SDLC] Software Development Life Cycle.
    \item[LMS]  Learning Management System.
    \item[LAMP] Linux, Apache, MySQL, PHP.
    \item[KRI] Kurdistan Region of Iraq
    \item[UI]   User Interface.
    \item[SQL] Standard Query Language.
    \item[CSS] Cascading Style Sheets.
    \item[HTML] HyperText Markup Language.
    \item[JS] JavaScript.
    \item[PC] Personal Computer.
    \item[LATEX] Lamport's TeX.
    \item[API] Application Programming Interface.
    \item[EARD] Entity Attribute Relationship Diagram.
    \item[WBS] Work Breakdown Structure.
    \item[JWT] JSON Web Token.
    \item[UML] Unified Modeling Language.
    \item[B2C] Business to Consumer.
    \item[AWS] Amazon Web Services.
    \item[MVC] Model View Controller.
    \item[JSON] JavaScript Object Notation.
    \item[OOP] Object Oriented Programming.
    \item[DBMS] Database Management System.
    \item[RDBMS] Relational Database Management System.
    \item[ORM] Object Relational Mapping.
    \item[ORMDBMS] Object Relational Mapping Database Management System.
    \item[FIP-UMMU] Fakultas Ilmu Pendidikan Universitas Muhammadiyah Maluku Utara.
    \item[RTM] Requirements Traceability Matrix
    \item[MVP] Minimum Viable Product
    \item[CORS] Cross-Origin Resource Sharing
    \item[IETF] Internet Engineering Task Force
    \item[CRUD] Create, Read, Update, Delete
    \item[SDK] Software Development Kit
    \item[DOM] Document Object Model
    \item[FSM] Finite State Machine
    \item[JSONB] JavaScript Object Notation Binary
    \item[CI/CD] Continuous Integration/Continuous Delivery
    \item[YAML] Yet Another Markup Language
    \item[UAT] User Acceptance Testing
    \item[CLI] Command Line Interface

\end{leftitemize}

\clearpage