\chapter{Implementation and Testing}

\begin{justify}
    This chapter delves into the Implementation, Testing, and Deployment phases of the software development process. Each of these phases plays a crucial role in bringing the project from conceptualization to realization. In this chapter, we will explore these phases in detail, examining the key activities and considerations involved in each.


    \vspace{0.25cm}
    \newendline The Implementation phase focuses on translating the design specifications into a functional software system. This involves writing code, configuring databases, integrating modules, and implementing various components that collectively bring the envisioned system to life. We will delve into the specific aspects of backend and frontend implementation, discussing the technologies used, validation mechanisms, controllers, models, database management, security practices, and more.


    \vspace{0.25cm}
    \newendline Following the implementation, the Testing phase ensures that the software meets the expected standards of quality, functionality, and reliability. We will explore the different types of tests conducted, such as unit tests, integration tests, and automated tests, to validate the system's behavior, uncover defects, and ensure smooth performance across various scenarios.


    \vspace{0.25cm}
    \newendline Once the software has successfully passed the testing phase, it proceeds to the Deployment phase, where it is made available to end-users. This phase involves setting up the necessary infrastructure, configuring servers, deploying the application, and addressing any compatibility or performance issues that may arise during the deployment process. We will examine the steps involved in deploying both the backend and frontend components, ensuring a smooth and seamless transition to the production environment.
\end{justify}
\clearpage

\input{chapters/sdlc/4-implementation}

\input{chapters/sdlc/5-testing}

\input{chapters/sdlc/6-deployment}