\chapter{Conclusion}

\begin{justify}
    This chapter is the Conclusion chapter of this thesis. Summary, Improvements, and Future Works are all integral parts of this chapter and they are as follows.\\
\end{justify}

\section{Summary}
\begin{justify}
    The development of this web application is a major step forward in the effort to automate the STDC's previously manual procedures at UKH. The primary objective of the project was achieved completely, and a functional and aesthetically pleasing program was developed as a result. The STDC's operations are streamlined, efficiency is increased, and communication is improved as a result of the application's automation of the workflow.

    \vspace{0.25cm}
    \newendline Implementing a good strategy for the development of the STDC was carefully organized and  the project led to its success. However, keep in mind that developing software is an iterative process that requires regular maintenance and improvements to accommodate shifting needs and new technologies.
    
    \vspace{0.25cm}
    \newendline The importance of re-engineering routine and mundane business processes is one of the many takeaways from this work. Improvements in effectiveness, precision, and usability are just some of the outcomes that can result from automating these processes with software. This project is a great example of how technology can be used to improve upon established procedures for the good of all concerned.
    
    \vspace{0.25cm}
    \newendline Stakeholder management, technical complexity, and insufficient resources were just a few of the problems that cropped up throughout the project's duration. Overcoming these challenges called for flexibility, the ability to think carefully, and open lines of communication. In spite of all of these obstacles, the project team was able to deliver a fully operational application that meets all of the specified goals.
    
    \vspace{0.25cm}
    \newendline The knowledge and skills acquired during this project have been invaluable. Understanding of software engineering principles, project management, and stakeholder collaboration were all enhanced. Working on a real-world project like automating the STDC's workflow allowed for practical application of theoretical concepts and best practices, which was invaluable.
    
    \vspace{0.25cm}
    \newendline In conclusion, the completion of this project is a major step toward the launch of a fully operational web application that will help automate the manual workflow currently in place at the UKH STDC. It highlights the benefits of digitizing business workflows and the iterative nature of software development. The successful completion of this project indicates the STDC's longevity and for its ongoing development and implementation of the application's features.\\
\end{justify}



\section{Future Works}

\begin{justify}
    There are a number of ways in which the STDC application can be enhanced in the near future. First, a more modern and aesthetically pleasing portal could help the application appeal to a wider audience and encourage more students to sign up for the STDC. Adding a "About Us," "Contact Us," and a "Frequently Asked Questions" page would be necessary to have in the STDC.

    \vspace{0.25cm}
    \newendline One other area of concentration is to improve the UI. The app can be made more user-friendly and aesthetically pleasing by adjusting the layout, and integrating intuitive features.

    \vspace{0.25cm}
    \newendline For the sake of the application's long-term maintainability, fixing the code quality issues is essential. The codebase needs to be reorganized to cut down on duplication and boost documentation. Because of this, the code will be more readable and understandable.

    \vspace{0.25cm}
    \newendline Since the current Windows Live login is no longer supported, it is crucial that the authentication method be modernized. A more robust and up-to-date authentication system that follows industry standards can be obtained by switching to Azure AD.

    \vspace{0.25cm}
    \newendline An in-app notification system will keep users aware of any developments at the STDC center. Future work on these aspects of the STDC app will allow it to grow into a more powerful and intuitive tool for users.
\end{justify}

\clearpage

